/*
I am a student who lives in Kolkata city with my family. All my friends are from the city too. Like many people who are residents of the town, my family also has migrated from North India to come and settle here. I did my schooling in 12th in a school in the city.
                <br>
                Now I’m doing my bachelor’s in the town.
                <br>
                Hobbies: Each person has different hobbies, and doing different things gives them joy. Baking is something that gives me comfort and helps me relax. I tried baking after entering college. At first, it was a little stressful, but then I started learning more and more. After a hectic day at college, it helps to relax you. Another thing that helps me relax is reading books. I started reading books when I was in school, and over the years, the habit is something that has helped me learn a lot.
                <br>
                Dreams and aspirations: While many people have dreams of becoming doctors and lawyers, I have always wanted to be a traveler. I don’t remember when I fell in love with traveling, but over the years, my passion for traveling has increased. Over the past few months, I have started living this dream, and it gives me so much joy.
                <br>
                My parents have always supported my dreams and aspirations. According to them, the only way to achieve all your goals is to work very hard and never give up on them. They have never imposed themselves and demanded that any of their children become what they want us. Instead, they wanted my siblings and me to choose careers and a life that will give us joy and stability.
                <br>
                Things I want to learn: There are many things I have to learn and want to learn. The first thing that I want to learn is cooking. The number of things I can make in the kitchen is limited. However, while making those things, I realize the happiness and satisfaction are get from cooking. One of the cuisines I want to learn correctly is Mexican. It’s a cuisine that I have started loving, and knowing how to cook dishes in the kitchen will make me happy.
                <br>
                Two more things that I want to learn are scuba diving and sky diving. I love doing adventurous things because they make give a feeling of thrill. I want to do professional courses in both the adventure activities.
            </div>

            */